### 2019-12-08 Common/chapters/medical.tex
Julien and Johan: describe medical imaging

\subsection{Types}

\subsubsection{MRI}

\subsubsection{CT}

\subsubsection{Mammography}

>>>>

Multiple types of medical imaging exist. The most commonly used to detect cancer are Magnetic Resonance Imaging (MRI), CT (Computed Tomography) scans
%, PET (Positron Emission Tomography) scans
and mammographies.

MRI relies on magnetic fields to provide a three-dimensional view of body parts, which allows to see the outputed images as a volume. Different settings, usually called sequences, make the look of the output vary, as shown on figure \ref{fig:PROSTATEx-t2-adc-dwi}.
Unlike MRI, CT is based on X-rays instead of magnetic fields, but still provides a three-dimensional representation of a body part. Figure \ref{fig:visualize_lung_dcm} shows a lung CT scan.

\begin{figure}[!h]
\centering
\includegraphics[width=1\textwidth, keepaspectratio=true]{./figures/PROSTATEx-t2-adc-dwi.png}
\caption{MRI - PROSTATEx - From left to right: T2-weighted, ADC and DWI}
\label{fig:PROSTATEx-t2-adc-dwi}
\end{figure}
